---
title: "Oblig 5"
author: "Sigbjørn Fjelland"
date: "10/29/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\underline{Problem 8.1}
```{r}
set.seed(123)
lb<-0.5
delta<-0.1
N<-c(10, 100, 1000)

T1<-rpois(N[1],lb)
S1<-rep(0,N[1])
S1[1]<-T1[1]

for(k in 2:N[1]) S1[k]<- S1[k-1] + T1[k]

tmax1<- S1[N[1]]+ 0.5/lb
tvalues1<-seq(delta, tmax1,delta)
ntvalues1<- length(tvalues1)
X1<-rep(0, ntvalues1)
for(t in 1: ntvalues1) X1[t]<- length( which( S1<=tvalues1[t] ))
plot(tvalues1, X1, type="s", main = 'Problem 8.1 (a) --> N = 10')
```
\newpage
```{r}
set.seed(123)
T2<-rpois(N[2],lb)
S2<-rep(0,N[2])
S2[1]<-T2[1]

for(k in 2:N[2]) S2[k]<- S2[k-1] + T2[k]

tmax2 <- S2[N[2]]+ 0.5/lb
tvalues2<-seq(delta, tmax2, delta)
ntvalues2<- length(tvalues2)
X2<-rep(0, ntvalues2)
for(t in 1: ntvalues2) X2[t]<- length( which( S2<=tvalues2[t] ))

plot(tvalues2, X2, type="s", main = 'Problem 8.1 (b) --> N = 100')
```
\newpage
```{r}
set.seed(123)
T3<-rpois(N[3],lb)
S3<-rep(0,N[3])
S3[1]<-T3[1]

for(k in 2:N[3]) S3[k]<- S3[k-1] + T3[k]

tmax3 <- S3[N[3]]+ 0.5/lb
tvalues3<-seq(delta, tmax3,delta)
ntvalues3<- length(tvalues3)
X3 <-rep(0, ntvalues3)
for(t in 1: ntvalues3) X3[t]<- length( which( S3<=tvalues3[t] ))
plot(tvalues3, X3, type="s", main = 'Problem 8.1 (c) --> N = 1000')
```

\newpage
d) 

```{r}
set.seed(123)
POI<-rpois(n=1000 ,lambda=lb)
S <-rep(0,N[2])
S[1]<-POI[1]
for(k in 2:N[2]) S[k]<- S[k-1] + POI[k]

tmax<- S[N[2]]+ 0.5/lb
tvalues<-seq(delta, tmax,delta)
ntvalues<- length(tvalues)
X<-rep(0, ntvalues)
for(t in 1: ntvalues) X[t]<- length( which( S<=tvalues[t] ))
plot(tvalues, X, type="s",col= 'blue', main = 'Poisson(1000, 1/2) and  -->  N = 100')
lines(y=tvalues2, X2, type="s", col= 'green')

legend("topleft",
c("n=1000","N=100"),
fill=c("blue","green")
)
```
\newpage

\underline{Problem 8.2}

a)
The probability for a poisson distributed random variables is given by:
\newline
$\\P(X=k)=\frac{\lambda^{k}}{k!}\cdot exp(-\lambda)\\$
\newline
It is known that the mean rate is 3 messages pr hour such that
\newline
$E(X)=\lambda=3$ and the probability that X is 0 afer 1 hour is:
\newline
$\\P(X=0)=\frac{3^{0}}{0!}\cdot exp(-3) = 0.0497\\$
\newline
From $08:00 \rightarrow{12:00}$ it is 4 hours and since poisson is indipendent there is
4 random variables $\{X_1, X_2, X_3, X_4 \}$ wich gives us probability that X is 0 from
$08:00 \rightarrow{12:00}$:
\newline
$\\P((X_1= 0)\cap (X_2= 0) \cap (X_3= 0) \cap (X_4 = 0))\\=(\frac{3^{0}}{0!}\cdot e^{-3})^4=(e^{-3})^4\\=e^{-12}=\underline{\underline{6.14\cdot 10^{-6}}}\\$
\newline

b)
Since events is poisson distributed with time intervals $\{X_1, X_2,..., X_n \}$ hrs, and rate $E(X_n)=\lambda$ of 3 with non overlaping events, the distribution is exponential with expnential parameter $\lambda$:
\newline
$\\f(x)=\lambda\cdot e^{-\lambda X}=3\cdot e^{-3\cdot X}$
\newpage
```{r}
x <- seq(0, 4, 0.1)
plot(x, dexp(x, 3), type = "l",
     ylab = "", lwd = 3, col = "red")
legend("topright", c(expression(paste(, lambda)), "3"),
       lty = c(0, 1), col = c("red"), box.lty = 0, lwd = 2)
```

